Download data

### 2024-08-12 scripts/subsetDataforCrews.Rmd
writing

p <- '/media/steppe/hdd/EmpiricalSeedZones/data/geodata/rasters'
f <- file.path(p, list.files(p, pattern = 'tif$'))
eSTZs <- rast(f)
names(eSTZs) <- gsub('-.*tif$', '', basename(f))
eSTZs <- resample(eSTZs, example_rast, method = 'near')
rm(f, p)

@@

lapply(teams_list[13], project_maker, 
       admu = admin_boundaries, 
       target_species = spp_needed, 
       blm_surf = blm_surf, 
       fs_surf = usfs_surf, 
       fire = fire_perimeters, 
       invasive = invasives, 
       total_change = change_intensity, 
       occurrences = occurrences, 
       roads = roads, seed_transfer = STZ)

lapply(seniors_list[3],  project_maker,
       admu = admin_boundaries, intype = 'senior',
       target_species = spp_needed, 
       blm_surf = blm_surf, 
       fs_surf = usfs_surf, 
       fire = fire_perimeters, 
       invasive = invasives, 
       total_change = change_intensity, 
       occurrences = occurrences, 
       roads = roads, seed_transfer = STZ)

@@

p2ts <- '/media/steppe/hdd/SeedPhenology/data/processed/timestamps'
lapply(
  X = teams_list[13], # 5 throws an error
  FUN = phen_tabulator,
  path = p2ts, 
  admu = admin_boundaries, 
  target_species = spp_needed
  ) # row 67

>>>>

crs(example_rast) == crs(eSTZs)

p <- '/media/steppe/hdd/EmpiricalSeedZones/data/geodata/rasters'
f <- file.path(p, list.files(p, pattern = 'tif$'))
eSTZs <- rast(f[1])
plot(eSTZs)
plot(example_rast)
names(eSTZs) <- gsub('-.*tif$', '', basename(f[1]))

eSTZs1 <- resample(eSTZs, example_rast, method = 'near', threads = 16)
plot(eSTZs1)
rm(f, p)

@@

lapply(teams_list[c(7,13)], project_maker, 
       admu = admin_boundaries, 
       target_species = spp_needed, 
       blm_surf = blm_surf, 
       fs_surf = usfs_surf, 
       fire = fire_perimeters, 
       invasive = invasives, 
       total_change = change_intensity, 
       occurrences = occurrences, 
       roads = roads, seed_transfer = STZ)

lapply(seniors_list[3],  project_maker_original,
       admu = admin_boundaries, intype = 'senior',
       target_species = spp_needed, 
       blm_surf = blm_surf, 
       fs_surf = usfs_surf, 
       fire = fire_perimeters, 
       invasive = invasives, 
       total_change = change_intensity, 
       occurrences = occurrences, 
       roads = roads, seed_transfer = STZ)

@@

p2ts <- '/media/steppe/hdd/SeedPhenology/data/processed/timestamps'
lapply(
  X = teams_list[c(7,13)], # 5 throws an error
  FUN = phen_tabulator,
  path = p2ts, 
  admu = admin_boundaries, 
  target_species = spp_needed
  ) # row 67
